
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE)
```

# franc

> Detect the Language of Text

[![Linux Build Status](https://travis-ci.org/gaborcsardi/franc.svg?branch=master)](https://travis-ci.org/gaborcsardi/franc)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/gaborcsardi/franc?svg=true)](https://ci.appveyor.com/project/gaborcsardi/franc)
[![](http://www.r-pkg.org/badges/version/franc)](http://www.r-pkg.org/pkg/franc)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/franc)](http://www.r-pkg.org/pkg/franc)

Franc has no external dependencies and supports 310 languages; all
languages spoken by more than one million speakers. Franc is a port
of the JavaScript project of the same name, see
https://github.com/wooorm/franc.

## Installation

```{r eval = FALSE}
devtools::install_github("gaborcsardi/franc")
```

## Usage

```{r}
library(franc)
```

Simply supply the text, and franc detects its language:

```{r}
franc("Alle menslike wesens word vry")
franc("এটি একটি ভাষা একক IBM স্ক্রিপ্ট")
franc("Alle mennesker er født frie og")
head(franc_all("O Brasil caiu 26 posições"))
```

`und` is the `undefined` language, this is returned if the input is
too short (shorter than 10 characters by default).

```{r}
franc("the")
franc("the", min_length = 3)
```

You can provide a whitelist or a blacklist:

```{r}
franc_all("O Brasil caiu 26 posições",
    whitelist = c("por", "src", "glg", "spa"))
head(franc_all("O Brasil caiu 26 posições",
    blacklist = c("src", "glg", "lav")))
```

## Supported languages

The R version of franc supports 310 languages. By default only the
languages with more than 1 million speakers are used, this is 175
languages. The \code{min_speakers} argument can relax this, and allows
using more languages:

```{r}
head(franc_all("O Brasil caiu 26 posições"))
head(franc_all("O Brasil caiu 26 posições", min_speakers = 0))
```

## License

MIT © Gábor Csárdi, Titus Wormer, Maciej Ceglowski, Jacob R. Rideout
and Kent S. Johnson.
